---
title: "RNA Seq AMO-CFZ"
author: "Anna James-Bott"
output:
  html_document:
    theme: cosmo
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, cache = TRUE)
```

```{r libraries, include=FALSE}
library("DESeq2")
load("data_objects.RData")
```

# PCA plots 
2 Outliers were removed from 24 hour time point. DMSO (reference compound) and MAZ 18 (less active compound)

## 6 hour
```{r load_6, echo = FALSE, message = FALSE, warning = FALSE, fig.align="center", cache =TRUE}
plotPCA(rld, intgroup="Compound")
```
One of the NCP 22 samples may appear to be an outlier however it varies on PC2 which only accounts for 9% of the variance.

## 24 hour {.tabset}
### No outliers
```{r load_24, echo = FALSE, message = FALSE, warning = FALSE, fig.align="center", cache = TRUE}
plotPCA(rld24, intgroup="Compound")
```
One of the DMSO samples (reference compound) and one of the MAZ 18 samples (less active compound) excluded.

### Outliers included
```{r load_24_outliers, echo = FALSE, message = FALSE, warning = FALSE, fig.align="center", cache = TRUE}
rld24_o <- readRDS("rld24_o.rds")
plotPCA(rld24_o, intgroup="Compound")
```
PC2 accounts for differential expression between more active compounds and DMSO. PC1 affected by outliers.